Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-03-10 paper_dev/article_pp.tex
integrate Ian's changes

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Similar tests %like the one described for SAR data 
  are carried out
  for both types of polarimetric SAR
  on both AIRSAR and RADARSAT2 datasets.
The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
The practical and predicted distributions are again plotted to determine whether their visual match is close in each case. Fig. \ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets. It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response. Evidently the match is good for $d=2$.

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
While a good p-value does not ensure automatic acceptance of the model,
  consistently high p-values lend high level of confidence to the proposed model\cite{Kolmogoroff_1941_AMS_461}.

@@

with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}

@@

%section introduction
One of the main beneficial implications for this proposal is that:
  it allows the extension of many of existing SAR data processing technique toward POLSAR.
One example has already been presented in this paper,
  where existing SAR discrimination measures are extended towards POLSAR.
This section illustrates another example for a common technique in SAR speckle filters evaluation.

@@

%describe the technique
In SAR, the intensity ratio is routinely used in evaluating speckle filters.
Specifically, the ratio of the filtered output to the noisy input image represents the amount of noise removed.
The multiplicative ratio, however, is not well suited to digital image presentation, which is linear and additive in nature\cite{Medeiros_2003_IJRS}. 
Thus logarithmic transformation is applied to convert the multiplicative intensity-ratio into linear subtractive residuals.  
Apparently if the speckle filter is perfect, the ratio or residual images should only contain random noise.
Thus the evaluation method is simply confirming that the speckle filter has not removed any image features.

@@

%describe the experiment
Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.}.
  A square 700$\times$700 pixel patch is first extracted from the AIRSAR Flevoland data (partial polarimetry HH-HV),
  and the two POLSAR speckle filters are then applied to the patch.
The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif

@@

%describe the result
Fig \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that the evaluation technique is also workable for POLSAR speckle filters.
In particular, the residual images clearly show both POLSAR speckle filters'  distortion impact.

@@

%conclude the section
There are many similar SAR data processing techniques that may be adaptable to POLSAR. 
Due to space constraint, these applications, however, fall outside the scope of this paper.

@@

%What has been done?
This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution. %***IVM: Hai pls check this sentence!
The model has been validated for specific $d=2$ and $d=3$ cases using real-life partial and full POLSAR data.
The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
We have also shown an excellent match between the specific $d=1$ model and that for traditional SAR intensity,
  effectively bringing the existing SAR theories under the umbrella of this new model.

%What are the results? What are their advantages over others' results?
The main emphasis of this paper is to consider the POLSAR covariance matrix determinant, and its derivatives, as scalar and representative observables for the multi-dimensional POLSAR data.
Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
Its representative power is justified for the following reasons.
First, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
Second, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
Third, this observable also leads to the establishment of new discrimination measures for POLSAR data.
  %, which should increase the usability of this proposal.
And finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to any changes in polarization basis.

The detailed and mathematical explanation linking the SAR intensity and the POLSAR determinant has been presented in Section \ref{sec:sar_special_case_of_polsar}.
This paragraph offers another high-level and intuitive linkage.
That is the scalar determinant in POLSAR can be used to represent and compare the multi-dimensonal data,
  much in the same way that the scalar magnitude is used to represent and compare complex numbers.
Similar to the determinant, the magnitude observable is also scalar and is not lossless.
Besides the magnitude, another observable would be needed to fully represent a complex number.
For example, in a polar representation, an extra angle would be requried.
Still, to compare complex numbers, the magnitude is widely used as it can be shown to be invariant to a change in the reference frame.
Similar to the maginute, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
%while it may not be \textit{fully} representative of the POLSAR data, 
Thus the scalar observable is proposed to represent and distinguish the multi-dimensional dataset.

%What are their benefit?
There are several beneficial implications of the proposed approach presented in this paper.
Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
Hence many techniques applicable to SAR cannot be directly extended to POLSAR.
There lies the different beneficial implications of the proposed approach presented in this paper.
Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
  its main benefit is that it enables the convenient adaptation of many existing SAR data processing techniques for POLSAR data.
Two example application have already been presented in this paper. 
  In the first instance, existing SAR discrimination measures are extended towards POLSAR.
  While in the second case, existing technique to evaluate SAR speckle filters is also shown extensible towards POLSAR.
At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.

%What are their limitations? What problems this appears to solve, but actually is not?
Of course, the models proposed in this article also have their own limitations.
Firstly, they are based on the complex Wishart distribution
%Thus its applicability is also limited by that of its foundation,
%  that is the proposed theoretical model 
  which is only guaranteed to work for homogeneous areas.
Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value, such a reduction is unlikely to be lossless in the general case.

In this paper, the theoretical model has only been validated for partial ($d=2$) and full ($d=3$) monostatic POLSAR data,
%and hence What can be done next?
  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
Other possible extensions include
  investigating the applicability of the observables into POLSAR heterogeneous areas,
  as well as exploring the use of these generic models in conjunction with other target decomposition techniques
    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.  
%Other possible future work includes
%  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
%  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
%    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.

>>>>

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Similar tests %like the one described for SAR data 
  are carried out
  for both types of polarimetric SAR
  on both AIRSAR and RADARSAT2 datasets.
The look-number is estimated for each type of data and for each image~\cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
The practical and predicted distributions are again plotted to determine whether their visual match is close in each case. Fig. \ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets. It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response. Evidently the match is good for $d=2$.

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) in the standard Kolmogorov-Smirnov goodness-of-fit test between curves~\cite{Kolmogoroff_1941_AMS_461}, noted under each graph.
While a good p-value may not lead to automatic acceptance of the model,
  consistently high p-values lend a high level of confidence to the proposal.

@@

with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}

@@

%section introduction
One of the main beneficial implications for this proposal is that
  it allows the extension of many of existing SAR data processing technique toward POLSAR.
One example has already been presented in this paper,
  where existing SAR discrimination measures are extended towards POLSAR.
This section illustrates another example for a common technique in SAR, namely speckle filter evaluation.

@@

%describe the technique
The intensity ratio is routinely used in SAR to evaluate speckle filters.
Specifically, the ratio of the filtered output to the noisy input image represents the amount of noise removed.
The multiplicative ratio, however, is not well suited to digital image presentation, which is linear and additive in nature\cite{Medeiros_2003_IJRS}. 
Thus logarithmic transformation is applied to convert the multiplicative intensity-ratio into linear subtractive residuals.  
Apparently if the speckle filter is perfect, the ratio or residual images should only contain random noise.
Thus the evaluation method is simply confirming that the speckle filter has not removed any image features.

@@

%describe the experiment
Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
  this technique can be equally applied to evaluate POLSAR speckle filters.
To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters\footnote{While boxcar filtering may not be the most modern POLSAR speckle filter,
  it is chosen here because the focus of the experiment is not to find the best POLSAR speckle filter, but rather to serve as an easily reproducible example of how an existing technique in SAR data processing can be simply adapted for use with POLSAR data.}.
  A square 700$\times$700 pixel patch is first extracted from the AIRSAR Flevoland data (partial polarimetry HH-HV),
  and the two POLSAR speckle filters are then applied to the patch.
The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
At the same time, the residual is computed for both filters, and the original image patches are also displayed in the same figure.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visual evaluation of POLSAR boxcar 3$\times$3 vs. 5$\times$5 speckle filters on AIRSAR Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%endif

@@

%describe the result
From a visual examination of Fig \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}, the evaluation technique also appears workable for POLSAR speckle filters, since the residual images clearly reveal the distortion impact of both POLSAR speckle filters.

@@

%conclude the section
Many similar SAR data processing techniques may be adaptable to POLSAR in this way, however they are not explored here due to space constraints.

@@

%What has been done?
This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.
The model has been validated for specific $d=2$ and $d=3$ cases using real-life partial and full POLSAR data.
The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic versions of the SAR intensity-ratio.
We have also shown an excellent match between the specific $d=1$ model and that for traditional SAR intensity,
which effectively brings the existing SAR theories under the umbrella of this new model.

%What are the results? What are their advantages over others' results?
The main emphasis of this paper is to consider the POLSAR covariance matrix determinant, and its derivatives, as scalar and representative observables for the multi-dimensional POLSAR data.
Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
Its representative power is justified for the following reasons.
First, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
Second, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
Third, this observable also leads to the establishment of new discrimination measures for POLSAR data.
  %, which should increase the usability of this proposal.
And finally, similar to eigen-values, the determinant of the POLSAR covariance matrix is invariant to any changes in polarization basis.

The detailed and mathematical explanation linking the SAR intensity and the POLSAR determinant has been presented in Section \ref{sec:sar_special_case_of_polsar} but consider another high-level and intuitive linkage:
The POLSAR scalar determinant can be used to represent and compare the multi-dimensional data,
  much in the same way that the scalar magnitude is used to represent and compare complex numbers.
Similar to the determinant, the magnitude observable is also scalar and is not lossless.
Besides the magnitude, another observable would be needed to fully represent a complex number.
For example, in a polar representation, the angle would be required in addition to magnitude.
Despite this, magnitude is still widely used when comparing two complex numbers, as it can be shown to be invariant to a change in the reference frame.
In the same way, the determinant of the POLSAR covariance matrix, also scalar and invariant to a change of polarization basis, is useful despite not being \textit{fully} representative of the POLSAR data. 
Thus this scalar observable is proposed to represent and distinguish between multi-dimensional datasets.

%What are their benefit?
There are several beneficial implications of the proposed approach presented in this paper.
Currently, while the field of SAR is much more developed than the field of POLSAR,  the two fields remain quite distinct.
Hence many techniques applicable to SAR have not been directly extended to POLSAR.
The approach of this paper, by providing a scalar and representative model for POLSAR which generalizes the traditional model for SAR intensity, enables the convenient adaptation of many existing SAR data processing techniques for used with POLSAR data.
In fact, two example applications of the technique were presented in this paper. 
  In the first instance, existing SAR discrimination measures are extended towards POLSAR.
  While in the second case, existing technique to evaluate SAR speckle filters are shown to be extensible towards POLSAR.
At the same time, this provides a consistent theory to unify the seemingly disparate discrimination measure proposals for SAR and POLSAR data.

%What are their limitations? What problems this appears to solve, but actually is not?
Of course, it must be mentioned that the models proposed in this paper also have their own limitations.
Firstly, they are based on the complex Wishart distribution
%Thus its applicability is also limited by that of its foundation,
%  that is the proposed theoretical model 
  which is only guaranteed to work for homogeneous areas.
Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value, such a reduction is unlikely to be lossless in the general case.

In this paper, the theoretical model has only been validated for partial ($d=2$) and full ($d=3$) monostatic POLSAR data,
%and hence What can be done next?
  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferometric POLSAR data ($d=6$) as possible future work.
Other possible extensions include
  investigating the applicability of the observables into POLSAR heterogeneous areas,
  as well as exploring the use of these generic models in conjunction with other target decomposition techniques
    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.  
%Other possible future work includes
%  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
%  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
%    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.
